### 2021-04-11 Paper/Main.tex
starting evening grind

to determine the beta deciles for individual secutires a regression

\begin{equation}
    R_{it}^e = a_{i,t} + \beta_{i1,t}(R_{m,t}-R_{rf,t})+\beta_{i2,t}(R_{m,t-1}-R_{rf,t-1})+\epsilon_{i,t}
\end{equation}
\begin{equation}
    \beta_{sum} = \sum_{k=1}^2\beta_{ik,t}
\end{equation}

>>>>

To determine the beta deciles for individual securities first a beta must be calculate for each security. To calculate the betas, a  simple regression outlined in equation \eqref{prerank_reg} was preformed. In this regression, a vector of  excess market returns in the current period and a vector of market returns from the previous period is regressed on a vector of current periods individual stock excess returns (i.e $R_{i,t}-R_{rf,t}$). The time movements for the data moved in month increments and the length of the vector ranged for 12 month to 60 months depending on the availability of data. Next, the beta values are summed together to get the pre-ranking beta value.

\begin{equation}
    R_{i,t}^e = a_{i,t} + \beta_{i1,t}(R_{m,t}-R_{rf,t})+\beta_{i2,t}(R_{m,t-1}-R_{rf,t-1})+\epsilon_{i,t}
    \label{prerank_reg}
\end{equation}
\begin{equation}
    \beta_{sum} = \sum_{k=1}^2\beta_{ik,t}
\end{equation}

Before assigning the deciles a data cleaning process was applied. A small portion of prerankning beta's are far larger than would be expected, as such these vales were removed from the sample by removing top and bottom 4\% of companies by preranking beta. A similar data cleaning process was also conducted in the Fama french five factor model. In addition to removing the very large and very small preranking beta values I also removed the companies with market capitalization less than 10M dollars in market capitalization. After sorting by the beta decile's size deciles were asigned based on the CRSP NYSE/NYSE American/NASDAQ market capitalization.
